An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
1

	\subsection{Vector Libraries and Databases}
The vector library and databases discussed in the following are not explicitly designed for hybrid query, but they support both attribute filtering and range filtering.

Faiss is an efficient similarity search library. It uses an ID selector to filter data before performing approximate nearest neighbor search. This supports hybrid search.In Faiss, we use the HQI batch optimization strategy in the IVF index. It groups queries with the same filter conditions. Each group only runs the filter once. It uses efficient matrix operations to compute vector similarity in batches.

PASE is a vector index plugin for PostgreSQL. It uses a "search first, then filter" strategy. But because the candidate set size is fixed, it may not return enough top-k results.

VBASE is also a vector plugin for PostgreSQL. It applies filters during the HNSW index traversal. This ensures enough results.

Milvus is a vector database built for large-scale similarity search. It filters data first, then performs approximate nearest neighbor search. This supports hybrid search.

@@

	\textcolor{violet}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512. \textcolor{orange}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets. Notably, the VBASE and PASE algorithms only support single-threaded construction.}

@@

\textit{\textbf{Index construction time.}}
%\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$. PASE and VBASE only support single-threaded builds. PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency. VBASE uses full-memory builds and is relatively faster. ACORN-$\gamma$  has a high computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates. Its build time on some datasets even exceeds that of single-threaded VBASE. }
\textcolor{orange}{On the regular-scale datasets (Figure~\ref{fig:build_time_comparison_query1}, left), among the algorithms limited to single-threaded construction, PASE has the longest build time. This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency. In contrast, VBASE uses full-memory builds and is therefore comparatively faster. Among the multi-threaded algorithms, ACORN-$\gamma$ is the slowest because it needs to expand the neighbor list and evaluate a large number of candidates. Its build time on some datasets even exceeds that of the single-threaded VBASE. }

\textcolor{orange}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1}, right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (Filtered-DiskANN, StitchedVamana and UNG) exhibit significantly increased construction time. This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead. In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size.This is because their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}

@@

\textit{\textbf{Index size.}}
\textcolor{orange}{
	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata. For regular-scale datasets, other methods show moderate variation. However, on large-scale dataset, Graph-based algorithms such as ACORN, Filtered-DiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain. Overall, IVF-based methods tend to produce more compact indexes.
}

@@

%\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
\textit{\textbf{Build peak memory.}}
% As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
% %on small-scale datasets, all methods except NHQ exhibit low memory usage. 
% \textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
% This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead. 
% 
% On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms. \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index. }.
\textcolor{orange}{As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size. Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets. However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size.}

\textcolor{orange}{
In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index. This leads to high peak memory usage during construction, despite the relatively small size of the final index.}

\textit{\textbf{Search peak memory.}}
%  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
%\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase. However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets. In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
\textcolor{orange}{
Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data. As a result, peak memory usage during querying is generally slightly lower than during construction. However, exceptions exist. As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.}

@@

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. CAPS performs as well as Puck. In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons. First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal. Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

@@

		We conduct experiments on the Text2image-Mix dataset. This dataset contains image and text vectors and is a hybrid multi-modal dataset. As shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.

@@

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. \textcolor{orange}{Notably, for regular-scale datasets, all algorithms build indexes using a single thread. For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}

@@

	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}}
	\textcolor{blue}{
		Similar to attribute filtering, the performance of multi-modal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets.
%		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}. As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets.
		}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
	& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
	& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
%	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
	\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
	\hline
\end{tabular}
	}
	\vspace{1mm}
\begin{flushleft}
	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
\end{flushleft}
	\centering

@@

\textcolor{orange}{The two variants of Filtered-DiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries. FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios. However, its disk-based construction significantly increases indexing time, and its performance is highly sensitive to attribute distribution. In contrast, StitchedVamana offers better search performance but performs poorly on 100M-scale datasets and OOD datasets.}

@@

	\subsection{Challenges}
	\subsubsection{\textbf{Attribute Filtering}}
	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency. Filtered-DiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments. Moreover, the index construction phase of graph-based algorithms is computationally intensive. Therefore, exploring GPU-based acceleration for graph construction and vector computation during indexing is promising. It can significantly improve the performance of graph-based methods.

>>>>

	\subsection{Vector Libraries and Databases}
	Many existing vector libraries, such as Faiss, and databases, such as Milvus, VBASE, and PASE, are designed specifically for ANN search, but they also support attribute filtering and range queries. We also experimented with them. However, since these libraries and databases do not rely on a single algorithm, their internal implementations are complex, using multiple methods and have detailed third-party documentation, so we will not elaborate on them here.

@@

	\textcolor{violet}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512. \textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets. Notably, the VBASE and PASE algorithms only support single-threaded construction.}

@@

\textit{\textbf{Index construction time.}}
%\textcolor{orange}{Among the regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the methods with longest build times are mainly PASE, VBASE, and ACORN-$\gamma$. PASE and VBASE only support single-threaded builds. PASE is the slowest because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency. VBASE uses full-memory builds and is relatively faster. ACORN-$\gamma$  has a high computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates. Its build time on some datasets even exceeds that of single-threaded VBASE. }
\textcolor{red}{On the medium-scale datasets (Figure~\ref{fig:build_time_comparison_query1} left), among the algorithms limited to single-threaded construction, PASE has the longest build time. This is because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency. In contrast, VBASE uses full-memory builds and is therefore comparatively faster. Among the multi-threaded algorithms, ACORN-$\gamma$ is the slowest because it needs to expand the neighbor list and evaluate a large number of candidates. Its build time on some datasets even exceeds that of the single-threaded VBASE. }

\textcolor{red}{On the large-scale dataset Deep100M (Figure~\ref{fig:build_time_comparison_query1} right), in addition to the three methods already mentioned, we also observe that algorithms based on Vamana (FilteredDiskANN, StitchedVamana and UNG) exhibit significantly increased construction time. This is because Vamana adopts a two-pass graph construction and optimization strategy (greedy search + robust pruning), resulting in extremely high computational overhead. In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size.This is because their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}

@@

\textit{\textbf{Index size.}} As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata. For medium-scale datasets, other methods show moderate variation. However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain. Overall, IVF-based methods tend to produce more compact indexes.

@@

%\underline{Faiss generates slightly smaller indexes due to its efficient index design}.
\textit{\textbf{Build peak memory.}}
% As shown in Figure~\ref{fig:build_memory_mb_comparison}, 
% %on small-scale datasets, all methods except NHQ exhibit low memory usage. 
% \textcolor{orange}{NHQ has the highest peak memory usage on almost all datasets.}
% This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead. 
% 
% On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms. \textcolor{orange}{The reason is that CAPS avoids redundant storage and graph structure overhead through hierarchical partitioning and AFT, and achieves a compact, sparse and controllable index. }.
As shown in Figure~\ref{fig:build_memory_mb_comparison}, the build peak memory usage is generally correlated with the sum of the index size and the dataset size. Algorithms that consume more peak memory during construction typically produce larger index sizes, and this trend holds across different datasets.

\textcolor{red}{However, PASE breaks this pattern due to its on-demand loading strategy, resulting in peak memory usage even lower than the final index size. 
In addition, NHQ generates a large number of candidate neighbors during the construction phase, but retains only a small subset for each point in the final index. This leads to high peak memory usage during construction, despite the relatively small size of the final index.}

\textit{\textbf{Search peak memory.}}
%  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
%\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase. However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets. In contrast, Milvus has lower peak memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data. As a result, peak memory usage during querying is generally slightly lower than during construction. However, exceptions exist. As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set.

@@

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	\textcolor{red}{
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for their superior performance is that they filter out irrelevant results during the retrieval process rather than searching for more candidates. In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify two primary reasons. First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal. Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.}
	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

@@

		We conduct experiments on the Text2image-Mix dataset. This dataset contains image and text vectors and is a hybrid multimodal dataset. As shown in Figure~\ref{fig:attribute-multimodal}, UNG and NHQ consistently perform best, followed by CAPS.

@@

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. \textcolor{orange}{Notably, for medium-scale datasets, all algorithms build indexes using a single thread. For the large-scale dataset Deep100M, all algorithms use 64 threads for index construction to improve efficiency, except DSG, which only supports single-threaded construction.}

@@

	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}}
	\textcolor{blue}{
		Similar to attribute filtering, the performance of multimodal range filtering queries shown in Figure~\ref{fig:range-multimodal} also aligns with the single-modality results in Figure~\ref{fig:exp_8_2}. These algorithms on the Text2Image dataset exhibit a significant performance degradation. This is because these range query algorithms are almost entirely graph-based, and graph algorithms require more iterations to find true neighbors in OOD datasets.
%		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}. As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets.
		}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
	& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
	& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
	\textbf{Robust to MultiModal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
%	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
	\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
	\hline
\end{tabular}
	}
	\vspace{1mm}
\begin{flushleft}
	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
\end{flushleft}
	\centering

@@

\textcolor{orange}{The two variants of FilteredDiskANN (FilteredVamana and StitchedVamana) support only single-attribute queries and multi-attribute OR queries. FilteredVamana supports dynamic insertion and disk-based indexing, making it suitable for memory-constrained scenarios. However, its disk-based construction significantly increases indexing time, and its performance is highly sensitive to attribute distribution. In contrast, StitchedVamana offers better search performance but performs poorly on 100M-scale datasets and OOD datasets.}

@@

	\subsection{Challenges}
	\subsubsection{\textbf{Attribute Filtering}}
	Most existing attribute filtering algorithms are graph-based, they typically outperform other methods in terms of query accuracy and efficiency. FilteredDiskANN leverages disk-based storage, making it more suitable for extremely large-scale datasets even in memory-constrained environments. Moreover, the index construction phase of graph-based algorithms is computationally intensive. Therefore, exploring GPU-based acceleration for graph construction and vector computation during indexing is promising. It can significantly improve the performance of graph-based methods.
